{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-29 paper.tex
Added short section on complexity. To be revisited

>>>>

\subsection{Time and space complexity}

With $n$ the number of worlds and $m$ the number of operators in a network
$\mathcal{N}$, the worst-case (when every world is a parameter of every
operator) time complexity of creating or updating a node and propagating the
change across the network is $O(n \times m)$. This effectively corresponds to
the server performing $n \times m$ requests.  The space complexity is the same
(as clients own a copy of the worlds they monitor), except for mesh data whose
complexity is $O(1)$ (only the server stores the mesh data).
